\def \IntroWhatImLookingFor {\langstr
	{What I'm looking for:}
	{Ce que je recherche:}
}

\def \IntroGoal {\langstr
	{To challenge myself and grow in seniority. Have more \textbf{ownership} and develop the product end-to-end. A company where ICs are more \textbf{autonomous}}
	{Je cherche à me challenger et grandir en séniorité. Avoir plus d'\textbf{ownership} et développé le produit end-to-end. Une entreprise où les contributeurs sont plus \textbf{autonomes}}
}

\def \IntroGoalAlt {\langstr
	{Looking for a big technical challenge that involves computer science fundamentals, and collaborating and learning from colleagues.}
	{Looking for a big technical challenge and collaborating and learning from colleagues.}
}

\def \IntroWhoAmI {\langstr
	{Who Am I:}
	{Qui je suis:}
}
\def \IntroRole {\langstr{Software Engineer}{Ingénieur backend}}
\def \IntroXP {\langstr
	{Back end engineer in \textbf{Java} with 4 years of experience. Working on \textbf{distributed systems}}
	{Programmeur backend en \textbf{Java} avec 4 années d'expérience. Travaillant sur des \textbf{systèmes distribués}}
}
\def \IntroProg {\langstr
	{I'm an avid Linux user, always tinkering. Participating in different meetups about coding and chess.}
	{Utilisateur et fan de Linux, je bricole constamment. Je participe à différents meetup sur la programmation et sur les échecs}
}

\def \IntroNationality {\langstr
	{Dual \textbf{French Irish citizen}. Fully French/English bilingual.}
	{Double nationalité \textbf{française/irlandaise}. Bilingue en Français/Anglais}
}

\def \IntroLearning {\langstr
	{Outside of work, learning \textbf{Go} and writing Neovim plugins in \textbf{Lua}. Also doing some home networking labs.}
	{En dehors du travail, j'apprends \textbf{Go} et développe des plugins \textbf{Lua} pour Neovim. Je développe aussi un \textit{homelab} réseau}
}

\def \IntroJavaStrength {\langstr
	{Strong interest in performance optimisation and JVM internals. Explored tools like \textbf{JITWatch} and have dug into the \textbf{OpenJDK} source code to understand the standard library better (`System.nanoTime` vs `System.currentTimeMillis`)}
	{Strong interest in performance optimisation and JVM internals. Explored tools like \textbf{JITWatch} and have dug into the \textbf{OpenJDK} source code to understand the standard library better (`System.nanoTime` vs `System.currentTimeMillis`)}
}
